\papertitle

### 2014-03-20 final-report/paper.tex
Clean up

\begin{figure}[ht]
  \includegraphics[width=\columnwidth]{images/utilization_chart}
  \caption{The utilization chart.}
  \label{fig:utilization_chart}
\end{figure}

@@

The matrix chart representing aggregate communication between workers help uncover data skew
issues, as discussed in \S \ref{sec:eval}.

% We initially considered having a chord diagram\footnote{\url{http://bl.ocks.org/mbostock/4062006}} instead of a matrix
%for the aggregate communication chart. But feedback during the progress presentation session convinced us that
%a chord diagram would suffer from scalability problems. Adding an option for displaying a chord diagram remains
%part of future work.

\todo{is this figure necessary or is the figure in the evaluation section enough?}

\begin{figure}[!ht]
  \includegraphics[width=\columnwidth]{images/networkVis1}
  \caption{Worker communication matrix chart. Each cell represents the number of exchanged tuples between a
  pair of workers.}
  \label{fig:matrix}
\end{figure}

>>>>

\begin{figure}[ht]
  \includegraphics[width=\columnwidth]{images/utilization_chart}
  \caption{The utilization chart. The user can brush on either the small graph on top or the bottom graph. Brushing on the second chart zooms the chart.}
  \label{fig:utilization_chart}
\end{figure}

@@

The matrix chart representing aggregate communication between workers help uncover data skew
issues, as discussed in Section~\ref{sec:eval}.
